Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Clarify Re dependence
Mark (a) and (b) in perf-re-dep figure

Mean power and drag coefficients at $\lambda=1.9$ are plotted \textit{versus} the Reynolds
number in Figure~\ref{fig:perf-Re-dep}. Note that the large error bars for $C_P$
at low $Re$ are dominated by systematic error estimates for the torque
transducer, since torque values are at the lower end of its measurement range.
However, the uncertainty due to random error or repeatability remains relatively
low. There is a drastic improvement in $C_P$ with increasing Reynolds number at
lower values of the Reynolds number. The power coefficient then becomes essentially
$Re$-independent at $Re_D = 0.8 \times 10^6$, which corresponds to an
approximate average blade chord Reynolds number $Re_{c, \mathrm{ave}} = 2.1
\times 10^5$. This threshold is consistent with the behavior of the blade
boundary layer transitioning from laminar to turbulent, thereby promoting either
the suppression or reattachment of the laminar separation bubble
\cite{Lissaman1983}.

@@

\caption{UNH-RVAT measured mean power (\hl {left}) and drag (right) coefficients at
 $\lambda=1.9$ plotted \textit{versus} the Reynolds number. Error bars indicate expanded
 uncertainty estimates for 95\% confidence, which for $C_P$ is dominated by
 systematic error estimates from the torque transducer operating at the lower end
 of its measurement range.}

%please use (a) and (b) to instead left and right and mark (a) and (b) in the figure.

>>>>

Mean power and drag coefficients at $\lambda=1.9$ are plotted \textit{versus}
the Reynolds number in Figure~\ref{fig:perf-Re-dep}. Note that the large error
bars for $C_P$ at low $Re$ are dominated by systematic error estimates for the
torque transducer, since torque values are at the lower end of its measurement
range. However, the uncertainty due to random error or repeatability remains
relatively low. There is a drastic improvement in $C_P$ with increasing Reynolds
number at the lower end of the $Re$ range. The power coefficient then becomes
essentially $Re$-independent at $Re_D = 0.8 \times 10^6$, which corresponds to
an approximate average blade chord Reynolds number $Re_{c, \mathrm{ave}} = 2.1
\times 10^5$. This threshold is consistent with the behavior of the blade
boundary layer transitioning from laminar to turbulent, thereby promoting either
the suppression or reattachment of the laminar separation bubble
\cite{Lissaman1983}.

@@

\caption{UNH-RVAT measured mean power \textbf{(a)} and drag \textbf{(b)}
    coefficients at $\lambda=1.9$ plotted \textit{versus} the Reynolds number. Error
    bars indicate expanded uncertainty estimates for 95\% confidence, which for
    $C_P$ is dominated by systematic error estimates from the torque transducer
    operating at the lower end of its measurement range.}
